### 2016-07-03 paper/introduction.tex
some work on section 2

Because equivalence of regular expressions is decideable, when
given a lens $\Lens$ with type $\Regex_1 \Leftrightarrow \Regex_2$,
it is easy to \emph{check} whether that lens also has type 
$\Regex_1' \Leftrightarrow \Regex_2'$, and lens programming languages
such as Boomerang \cite{foster:thesis} do so.  However, 
when we turn to synthesis and are given the lens type 
$\Regex_1' \Leftrightarrow \Regex_2'$ and the option to apply this
rule, the search space becomes unmanageably large.  In essence,
we must solve the problem of search \emph{in two dimensions}:  In one
dimension, we must search for a regular expression \emph{type}
with an appropriate ``syntactic shape'' and in a second dimension,
we must search for a lens expression that has the given type and
is consistent with the user's examples.

>>>>

Because equivalence of regular expressions is decideable, when
given a lens $\Lens$ with type $\Regex_1 \Leftrightarrow \Regex_2$,
it is easy to \emph{check} whether that lens also has type 
$\Regex_1' \Leftrightarrow \Regex_2'$, and lens programming languages
such as Boomerang \cite{foster:thesis} do so.  However, 
when we turn to synthesis and are given the lens type 
$\Regex_1' \Leftrightarrow \Regex_2'$ and the option to apply this
rule, the search space becomes unmanageably large --- we must guess
some arbitrary new lenses $\Regex_1$ and $\Regex_2$ that are
equivalent to  $\Regex_1'$ and $\Regex_2'$ respectively
and there are infinitely many such regular expressions to choose
from.  In essence,
we must solve the problem of search \emph{in two dimensions}:  In one
dimension, we must search for a regular expression \emph{type}
with an appropriate ``syntactic shape'' and in a second dimension,
we must search for a lens \emph{expression} that has the given type and
is consistent with the user's examples.
